\section{Reference}
\begin{thebibliography}{9}
    \bibitem{1}
    Arun Subramaniyan , Reetuparna Das. 2017.
    \textit{Parallel Automata Processor}. 
    ISCA ’17 Toronto,ON,Canada, June 24-28,2017
    \bibitem{2}
    Todd Mytkowicz, Madanlal Musuvathi, and Wolfram Schulte. 2014.
\textit{Data-parallel
finite-state machines.}In Architectural Support for Programming Languages and
Operating Systems, ASPLOS ’14, Salt Lake City, UT, USA, March 1-5, 2014.
    \bibitem{3}
    Chunkun Bo, Ke Wang, Jeffrey J Fox, and Kevin Skadron. 2015. Entity Resolution
    \textit{Acceleration using Micron’s Automata Processor.}
    Architectures and Systems for
    Big Data (ASBD), in conjunction with ISCA (2015).
    \bibitem{4}
    Ke Wang, Elaheh Sadredini, and Kevin Skadron. 2016. Sequential pattern mining
with the Micron automata processor. In\textit{Proceedings of the ACM International
Conference on Computing Frontiers.}ACM, 135–144.
\bibitem{5}
Sasa Misailovic, Michael Carbin, Sara Achour, Zichao Qi, and Martin C Ri-
nard. 2014. Chisel: Reliability-and accuracy-aware optimization of approximate
computational kernels. In ACM SIGPLAN Notices, Vol. 49. ACM, 309–328.
\bibitem{6}
Sutapa Datta and Subhasis Mukhopadhyay. 2015. \textit{A grammar inference approach
for predicting kinase specific phosphorylation sites.}PloS one 10, 4 (2015).
\bibitem{7}
Indranil Roy and Srinivas Aluru. 2016. \textit{Discovering motifs in biological sequences
using the micron automata processor.}
IEEE/ACM Transactions on Computational
Biology and Bioinformatics 13, 1 (2016),
\bibitem{8}
Todd Mytkowicz, Madanlal Musuvathi, and Wolfram Schulte. 2014.
\textit{Data-parallel
finite-state machines.}In Architectural Support for Programming Languages and
Operating Systems, ASPLOS ’14, Salt Lake City, UT, USA, March 1-5, 2014.
\bibitem{9}
Micron Automata Processing. Retrieved May 3, 2017 from http://www.
micronautomata.com/
\bibitem{10}
Alexandre Petrenko. 2001.
\textit{Fault model-driven test derivation from finite state
models: Annotated bibliography.}
In Modeling and verification of parallel pro-
cesses. Springer.
\bibitem{11}
Paul Dlugosch, Dave Brown, Paul Glendenning, Michael Leventhal, and Harold
Noyes. 2014.\textit{An efficient and scalable semiconductor architecture for parallel
automata processing.}IEEE Transactions on Parallel and Distributed Systems 25,
12 (2014).
\bibitem{12}
Micron Automata Processing D480 Software Development Kit. AP Flow
Concepts. Retrieved May 3, 2017 from http://micronautomata.com/apsdk\_
documentation/latest/h1\_ap.html

\end{thebibliography}